Parallel global optimization algorithm employing decision trees for launching local methods

### 2025-09-15 2025/MMST_DecisionTree/ParallelDecisionTree.tex
Поправлен перевод

\usepackage[utf8]{inputenc} % кодировка
\usepackage[english, russian]{babel} % Русские и английские переносы
\usepackage{cite}              % для корректного оформления литературы
\usepackage{enumitem}
\usepackage{amsmath}

@@

Fig. \ref{fig:fig2} shows the graph of the objective function $\varphi(y)$; Fig. \ref{fig:fig2_2} presents the corresponding approximation $\psi(y)$ constructed using a decision tree.
\begin{figure}
	\begin{center}
		\begin{minipage}[h]{0.75\linewidth}
			\includegraphics[width=1\linewidth]{figure/fig5.png}
			\caption{Graph of the benchmark objective function $\varphi(y)$} %% подпись к рисунку
			\label{fig:fig2}
		\end{minipage}
	\end{center}
\end{figure}

\begin{figure}
	\begin{center}
		\begin{minipage}[h]{0.75\linewidth}
			\includegraphics[width=1\linewidth]{figure/fig4.png}
			\caption{Graph of the piecewise-constant approximation $\psi(y)$ of the function $\varphi(y)$} %% подпись к рисунку
			\label{fig:fig2_2}
		\end{minipage}
	\end{center}
\end{figure}

@@

\begin{figure} 
	\begin{center} 
		\begin{minipage}[h]{1.0\linewidth} 
			\includegraphics[width=1\linewidth]{figure/fig1.pdf} 
			\caption{An example showing the iterations of the Hooke-Jeeves method} %%  подпись к рисунку 
			\label{fig:fig1} 
		\end{minipage} 
	\end{center} 
\end{figure}

@@

	\item Извлекаем из множества $U$ (координат точек испытания) $c = max(p, |U|)$ координат точек испытания $y^{k+1}=y\left(x^{k+1}\right) ... y^{k+c}=y\left(x^{k+c}\right)$. Если $c < p$ то сначала вычисляем $n = p - c$ точек согласно шагам 2 - 7, иначе сразу переходим к шагу 8.

@@

	\item Отправить на процесс $j, \ 1\leq j\leq n$ координату $y'^{k+1} ... y'^{k+n}$  и сообщить процессу, что нужно произвести одиночное испытание.

	\item Отправить на процессы $h, \ 1\leq h\leq c$ координаты точек $y^{k+1} ... y^{k+c}$ и сообщить процессу, что нужно запустить локальный метод.

	\item Получить со всех $p$ процессов значения испытаний и добавить их в поисковую информацию.

	\item Добавить точки испытаний $y'^{k+1}=y\left(x^{k+1}\right) ... y'^{k+n}=y\left(x^{k+т}\right)$ к множеству $V$.

	\item Если $k\ <\ 100 N$, перейти к шагу 1.

@@

	\item Вычислить кусочно постоянную аппроксимацию функции $\psi(y)$, по дереву решений : $Z' = \{ z'=  \psi(y'), y' \in Y'\}$

	\item Для всех точек $y'\in V$ найти точки $y'_q$, ближайшие к $y'$,

	Если ни одна точка $y'_q$ не имеет меньшего значения, чем $y'_q$, поместить $y'$ в множество $U$

	Очистить множество $V$.

	\item Проверка критериев остановки

>>>>

%\usepackage[utf8]{inputenc} % кодировка
\usepackage[english]{babel} % Русские и английские переносы
\usepackage{cite}              % для корректного оформления литературы
\usepackage{enumitem}
\usepackage{amsmath}

@@

Fig. \ref{fig:fig2} shows the graph of the objective function $\varphi(y)$; Fig. \ref{fig:fig2_2} presents the corresponding approximation $\psi(y)$ constructed using a decision tree.
\begin{figure}
	\begin{center}
		\begin{minipage}[h]{0.7\linewidth}
			\includegraphics[width=1\linewidth]{figure/fig5.png}
			\caption{Graph of the benchmark objective function $\varphi(y)$} %% подпись к рисунку
			\label{fig:fig2}
		\end{minipage}
	\end{center}
\end{figure}

\begin{figure}
	\begin{center}
		\begin{minipage}[h]{0.7\linewidth}
			\includegraphics[width=1\linewidth]{figure/fig4.png}
			\caption{Graph of the piecewise-constant approximation $\psi(y)$ of the function $\varphi(y)$} %% подпись к рисунку
			\label{fig:fig2_2}
		\end{minipage}
	\end{center}
\end{figure}

@@

\begin{figure} 
	\begin{center} 
		\begin{minipage}[!h]{1.0\linewidth} 
			\includegraphics[width=1\linewidth]{figure/fig1.pdf} 
			\caption{An example showing the iterations of the Hooke-Jeeves method} %%  подпись к рисунку 
			\label{fig:fig1} 
		\end{minipage} 
	\end{center} 
\end{figure}

@@

	\item Extract $c = \max(p, |U|)$ trial point coordinates $y^{k+1}=y\left(x^{k+1}\right) ... y^{k+c}=y\left(x^{k+c}\right)$ from the set $U$ (which contains trial point coordinates). If $c < p$, then first perform trials at $n = p - c$ points according to Steps~2--7; otherwise proceed directly to Step~8.

@@

	\item Send to process $j$, $1 \leq j \leq n$, the coordinates $y'^{k+1}, \dots, y'^{k+n}$ and notify the process that it needs to perform a single trial.

	\item Send to processes $h$, $1 \leq h \leq c$, the coordinates of points $y^{k+1}, \dots, y^{k+c}$ and notify the process that it needs to run a local method.

	\item Receive trial values from all $p$ processes and add them to the search information.

	\item Add the trial points $y'^{k+1}=y\left(x^{k+1}\right) , \dots, y'^{k+n}=y\left(x^{k+n}\right)$  to the set $V$.

	\item If $k < 100N$, go to Step~1.

@@

	\item Compute the piecewise constant approximation of the function $\psi(y)$ using the decision tree: $Z' = \{ z' = \psi(y'), y' \in Y' \}$.

	\item For all points $y' \in V$, find the points $y'_q$ closest to $y'$.

	If no point $y'_q$ has a value smaller than $y'$, add $y'$ to the set $U$.

	Clear the set $V$.

	\item Check the stopping criteria.
